Run aquaculture model for Atlantic salmon

### 2025-12-17 docs-working/07_run_atlantic_salmon_model.qmd
Changes for working on Nectar

library(arrow)
library(sf)
library(dplyr)
library(tidyr)
library(terra)
library(magrittr)
library(purrr)
library(furrr)
library(future)
library(tictoc)
library(ggplot2)
library(fs)
library(conflicted)
library(stringr)
library(readxl)
library(units)
library(qs)
library(here)
library(targets)
conflicted::conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)

@@

@@

Sys.setenv(TAR_PROJECT = "project_farmruns")

# tar_make(names = c("feed_params", "feed_names"))

tar_load(feed_params)
tar_load(feed_names)

@@

Sys.setenv(TAR_PROJECT = "project_farmruns")
# tar_validate()
# tar_prune()

# tar_make(test_reference_feed)
tar_load_globals()
reference_feed_name
tar_read(test_reference_feed) # if weight ~ 0 then feeds aren't processing properly
```

@@

Sys.setenv(TAR_PROJECT = "project_farmruns")

# Get harvest sizes for all farms
tar_make(names = contains(c("harvest_size", "feed_params")))
```

@@

harvest_size <- tar_read(harvest_size_chunked) %>% 
  bind_rows()

@@

Sys.setenv(TAR_PROJECT = "project_sensitivities")
# tar_validate()
# tar_visnetwork(targets_only = T)

tar_make(test_reference_feed)
tar_read(test_reference_feed) # if weight ~ 0 then feeds aren't processing properly, fix before proceeding
```

@@

Sys.setenv(TAR_PROJECT = "project_sensitivities")

tar_make(contains("spec"), seconds_meta_append = 300)
tar_make(contains("pop"), shortcut = T, seconds_meta_append = 300)
tar_prune()
```

@@

tar_load(sens_results_spec)
tar_load(sens_results_pop)

@@

sens_measures <- levels(sens_results$measure)
sens_results_figfiles <- file.path(output_sens_data_path, paste0("sens_plot_", sens_measures, ".qs"))
sens_results_figfiles2 <- file.path(output_sens_data_path, paste0("sens_plot_", sens_measures, ".png"))

for (sm in seq_along(sens_measures)) {
  p <- sens_results %>% 
    filter(measure == sens_measures[sm]) %>% 
    ggplot(aes(x = adj_param, y = mean_sens, ymin = mean_sens-sd_sens, ymax = mean_sens+sd_sens)) +
    geom_col(fill = "salmon", alpha = 0.65, colour = "black") +
    geom_errorbar(width = 0.5) +
    coord_flip() +
    theme_classic()
  qsave(p, sens_results_figfiles[sm])
  ggsave(sens_results_figfiles2[sm])
}
```

@@

Sys.setenv(TAR_PROJECT = "project_farmruns")

# Pre-run to reduce load
tar_make(
  names = contains(c("data", "feed")),
  seconds_meta_append = 90
)

# tar_outdated()

# Run results
tar_make(
  names = c("farm_run_chunked", "farm_full_results"), 
  seconds_meta_append = 120,
  shortcut = T # only if you've done the pre-run, above
)
```

@@

Sys.setenv(TAR_PROJECT = "project_farmruns")
farm_IDs_chunked <- tar_read(farm_IDs_chunked) %>% unname() %>% unlist()
tar_load(feed_names)

tar_load(farm_full_results)
total_ends <- bind_rows(lapply(farm_full_results, `[[`, "total_ends"))
cohort_results <- bind_rows(lapply(farm_full_results, `[[`, "cohort_results_daily"))

>>>>

library(tidyverse)
library(arrow)
library(sf)
library(terra)
library(furrr)
library(future)
library(tictoc)
library(fs)
library(conflicted)
library(readxl)
library(units)
library(qs)
library(here)
library(targets)
conflicted::conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)

@@

farm_script <- here("targets/_targets_farmruns.R")
farm_store <- here("targets/_targets_farmruns")
sens_script <- here("targets/_targets_sensitivities.R")
sens_store <- here("targets/_targets_sensitivities")

@@

# tar_make(names = c("feed_params", "feed_names"), script = farm_script, store = farm_store)

tar_load(feed_params, store = farm_store)
tar_load(feed_names, store = farm_store)

@@

# Sys.setenv(TAR_PROJECT = "project_farmruns")

tar_validate(script = farm_script, store = farm_store)
# tar_prune(script = farm_script, store = farm_store)

tar_make(test_reference_feed, script = farm_script, store = farm_store)
tar_load_globals(script = farm_script)
reference_feed_name
tar_read(test_reference_feed, store = farm_store) # if weight ~ 0 then feeds aren't processing properly
```

@@

# Sys.setenv(TAR_PROJECT = "project_farmruns")

# Get harvest sizes for all farms
tar_make(names = contains(c("harvest_size", "feed_params")), script = farm_script, store = farm_store)
```

@@

harvest_size <- tar_read(harvest_size_chunked, store = farm_store) %>% 
  bind_rows()

@@

# Sys.setenv(TAR_PROJECT = "project_sensitivities")
# tar_validate(script = farm_script, store = farm_store)
# tar_visnetwork(targets_only = T, script = farm_script, store = farm_store)

tar_make(test_reference_feed, script = sens_script, store = sens_store)
tar_read(test_reference_feed, store = sens_store) # if weight ~ 0 then feeds aren't processing properly, fix before proceeding
```

@@

# Sys.setenv(TAR_PROJECT = "project_sensitivities")

tar_make(contains("spec"), seconds_meta_append = 300, script = sens_script, store = sens_store)
tar_make(contains("pop"), seconds_meta_append = 300, script = sens_script, store = sens_store)
# tar_prune(script = sens_script, store = sens_store)
```

@@

tar_load(sens_results_spec, store = sens_store)
tar_load(sens_results_pop, store = sens_store)

@@

sens_measures <- levels(sens_results$measure)
sens_results_figfiles <- file.path(output_sens_data_path, paste0("sens_plot_", sens_measures, ".png"))

for (sm in seq_along(sens_measures)) {
  p <- sens_results %>% 
    filter(measure == sens_measures[sm]) %>% 
    ggplot(aes(x = adj_param, y = mean_sens, ymin = mean_sens-sd_sens, ymax = mean_sens+sd_sens)) +
    geom_col(fill = "salmon", alpha = 0.65, colour = "black") +
    geom_errorbar(width = 0.5) +
    coord_flip() +
    theme_classic()
  ggsave(sens_results_figfiles[sm])
}
```

@@

# Sys.setenv(TAR_PROJECT = "project_farmruns")

# Pre-run to reduce load
tar_make(
  names = contains(c("data", "feed")),
  script = farm_script, store = farm_store
)

# tar_outdated(script = farm_script, store = farm_store)

# Run whole pipeline
tar_make(
  seconds_meta_append = 300,
  script = farm_script, store = farm_store
)
```

@@

Sys.setenv(TAR_PROJECT = "project_farmruns")
farm_IDs_chunked <- tar_read(farm_IDs_chunked, script = farm_script, store = farm_store) %>% unname() %>% unlist()
tar_load(feed_names, script = farm_script, store = farm_store)

tar_load(farm_full_results, script = farm_script, store = farm_store)
total_ends <- bind_rows(lapply(farm_full_results, `[[`, "total_ends"))
cohort_results <- bind_rows(lapply(farm_full_results, `[[`, "cohort_results_daily"))
